Total Platform Cyber Protection

### 2016-06-07 paper.tex
finished writing dynamic analysis section, started on static analysis added few more papers to the bibliography

>>>>

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, and Binary Analysis~\cite{Song2008}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C/C++ languages~\cite{Younan2012}.

The other approach to analyze applications is Static Analysis~\cite{cousot1977abstract}, where the code is analyzed at compile time. There has been considerable research in this area, spanning across
